Seasonality of submesoscale dynamics in the Kuroshio Extension

### 2016-07-08 writeup/rocha_etal.tex
Updates figure3

@@

\begin{figure*}[ht]
  \begin{center}
    \includegraphics[width=1.\textwidth]{figs/fig3.pdf}
 \caption{Seasonal variation of joint probability distributions:  vorticity vs. strain rate (a through f).
          and vorticity vs. Laplacian of sea-surface height (g through l) in April (a through c;
          g  through i) and October (d through f;
          j  through l).
          Dashed lines in (a) through (e) represent pure strain flow $\alpha = \pm\zeta$,
          characteristic of fronts. Dashed lines in (f) through
          (l) represent geostrophic flow $\zeta = \frac{g}{f}\nabla_h^2 \eta$.}
 \label{fig3}
 \end{center}
\end{figure*}

@@

\begin{figure*}[ht]
  \begin{center}
    \includegraphics[width=.9\textwidth]{figs/fig4.pdf}
 \caption{Surface (horizontal) KE (a) and SSH variance wavenumber spectra (b)
 in the 1/48$^\circ$ simulation. Solid lines
 are spectra based on hourly snapshots, dashed lines are spectra based on daily-averaged
 fields.}
 \label{fig4}
 \end{center}
\end{figure*}

>>>>

\begin{figure*}[ht]
  \begin{center}
    \includegraphics[width=.95\textwidth]{figs/fig3.pdf}
 \caption{Seasonal variation of joint probability distributions:  vorticity vs. strain rate (a through d).
          and vorticity vs. Laplacian of sea-surface height (e through h) in April (a, b,
          e, f) and October (c, d, g, h).
          Dashed lines in (a) through (d) represent pure strain flow $\alpha = \pm\zeta$,
          characteristic of fronts. Dashed lines in (e) through
          (h) represent geostrophic flow $\zeta = \frac{g}{f}\nabla_h^2 \eta$.}
 \label{fig3}
 \end{center}
\end{figure*}

@@

@@

\begin{figure*}[ht]
  \begin{center}
    \includegraphics[width=.95\textwidth]{figs/fig4.pdf}
 \caption{Surface (horizontal) KE (a) and SSH variance wavenumber spectra (b)
 in the 1/48$^\circ$ simulation. Solid lines
 are spectra based on hourly snapshots, dashed lines are spectra based on daily-averaged
 fields.}
 \label{fig4}
 \end{center}
\end{figure*}
